Stack Safety as a Security Property

### 2021-02-14 rebuttal.txt

The local state encapsulation (LSE) part of the property we present
aims to characterize stack safety in security terms. For readers
familiar with integrity / confidentiality / noninterference, the eager
version should be fairly intuitive. The lazy/observable properties,
though less intuitive, are more interesting in that they precisely
characterize behaviors that would be considered violations to the more
intuitive view of stack safety but that can still be considered safe
by an external observer. The well-bracketed control flow (WBCF) part
simply formalizes standard behavior of stack-based control flow.

By contrast, [Skorstengaard 2019b] relies on different prior intuitions: for
readers familiar with operational models of stacks (here the
built-in oLCM stack), their property is more intuitive. For readers
versed in security theory, we believe that making an explicit connection
with integrity and confidentiality gives useful insight.

(2) Usefulness for reasoning:

Local state encapsulation enables reasoning about the behavior of a
function in a vacuum, without needing to account for either its
caller's state or for changes to its state during its callees. When
proving a property of a function, confidentiality allows us to only
reason about configurations of the stack frame itself (instead of all
possible memory configurations).  Moreover, while our threat model
permits a callee to execute arbitrary code, severely limiting our
ability to reason about the behavior of its caller after return,
integrity allows us to prove properties of the caller by quantifying
only over configurations of registers and memory above the stack.

In security terms, we make no guarantees about the callee's behavior,
but we can guarantee that it communicates with the caller only through
the approved interface.  In terms of a logic, integrity and
confidentiality would allow a procedure rule that states that local
variables do not change over calls (which basically says that
procedure calls are a no-op except for observations and the return
value), and that lemmas proved about procedure return values and
observations can be applied at call sites.

### 2021-02-14 main.tex
Progress on properties

\[\stackDom \in \STKDOMS ::= \outside + \unsealed + \sealed{n}\]
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS)
  \times (n \in \mathbb{N}) \]

An initial context \(\context_0 = \domMap_0 \times 0\) where \(\domMap_0\) maps
the stack to \(\unsealed\) and all other addresses and all registers to \(\outside\).
Then at each step we update the context according to the context-step function,
\(\stepsto_C\), which we will define in terms of the operations
\(\push{\domMap}{n}{\components}\), in which \(\components \subseteq \COMPONENTS\),
and \(\pop{\domMap}{n}\), pronounced ``push'' and ``pop'' and defined as follows.

\[
(\push{\domMap}{n}{\components}) ~ \component =
\begin{cases}
  \sealed{n} & \text{if } \domMap ~ \component = \unsealed
               \text{ and } \component \in \components \\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]
\[
(\pop{\domMap}{n}) ~ \component =
\begin{cases}
  \unsealed & \text{if } \domMap ~ \component = \sealed{n-1} \\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]

@@

\begin{center}
\begin{minipage}{.4\textwidth}
  \judgmenttwo{\(\mach \stepsto \mach'\)}
              {\(\codemap ~ (\mach ~ \PCname) = \funid, \mathbf{Some} ~ \callmap\)}
              {\(\mach,(\domMap,n) \stepsto_C \mach',(\push{\domMap}{n}{\sealcon ~ \mach},n+1)\)}
\end{minipage}
\hspace*{0.1\textwidth}
\begin{minipage}{.4\textwidth}
  \judgmenttwo{\(\mach \stepsto \mach'\)}
              {\(\codemap ~ (\mach ~ \PCname) = \funid, \mathbf{Some} ~ \retmap\)}
              {\(\mach,(\domMap,n) \stepsto_C \mach',(\pop{\domMap}{n},n-1)\)}
\end{minipage}
\end{center}

@@

@@

@@

>>>>

\[\stackDom \in \STKDOMS ::= \outside + \unsealed + \sealed{\depth}\]
\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS)
  \times (\depth \in \mathbb{N}) \]

An initial context \(\context_0 = \domMap_0, 0\) where \(\domMap_0\) maps
the stack to \(\unsealed\) and all other addresses and all registers to \(\outside\).
Then at each step we update the context according to the context-step function,
\(\stepsto_C\), which we will define in terms of the operations
\(\push{\domMap}{n}{\components}\), in which \(\components \subseteq \COMPONENTS\),
and \(\pop{\domMap}{n}\), pronounced ``push'' and ``pop'' and defined as follows.

\[
(\push{\domMap}{n}{\components}) ~ \component =
\begin{cases}
  \sealed{\depth} & \text{if } \domMap ~ \component = \unsealed
                    \text{ and } \component \in \components \\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]
\[
(\pop{\domMap}{n}) ~ \component =
\begin{cases}
  \unsealed & \text{if } \domMap ~ \component = \sealed{\depth-1} \\
  \domMap ~ \component & \text{else} \\
\end{cases}
\]

@@

\begin{center}
\begin{minipage}{.4\textwidth}
  \judgmenttwo{\(\mach \stepsto \mach'\)}
              {\(\codemap ~ (\mach ~ \PCname) = \funid, \mathbf{Some} ~ \callmap\)}
              {\(\mach,(\domMap,\depth) \stepsto_C \mach',(\push{\domMap}{\depth}{\sealcon ~ \mach},\depth+1)\)}
\end{minipage}
\hspace*{0.1\textwidth}
\begin{minipage}{.4\textwidth}
  \judgmenttwo{\(\mach \stepsto \mach'\)}
              {\(\codemap ~ (\mach ~ \PCname) = \funid, \mathbf{Some} ~ \retmap\)}
              {\(\mach,(\domMap,\depth) \stepsto_C \mach',(\pop{\domMap}{\depth},\depth-1)\)}
\end{minipage}
\end{center}

@@

Our first property will be {\em ultra eager}, meaning that it will be quantified over each step
of execution from any initial state. The criterion for integrity is simple: sealed components do not
change.

\definition A system enjoys {\em ultra-eager integrity} if, for any initial state \(\mach_0\),
its initial context \(\context_0\), and its initial policy state \(\pol_0\), and each
pair of adjacent states \(\mach,(\domMap,\depth),\pol \stepsto_C \mach',\context',\pol'\) in
the induced trace from \(\mach_0,\context_0,\pol_0\), if \(\domMap ~ \component = \sealed{\depth'}\)
for any \(\depth'\), then \(\mach(\component) = \mach'(\component)\).

@@

\definition Call Rule goes here.

\definition A system enjoys {\em eager integrity} if, for any initial state \(\mach_0\), initial
context \(\context_0\), and initial policy state \(\pol_0\) and any call depth \(\depth\), each segment
\(\MCPTrace\) taken from the induced trace from \(\mach_0,\context_0,\pol_0\) by
\(\prop (\domMap,\depth') = \depth' \geq \depth\) satisfies \(\pi_m(\head ~ \MCPTrace) \component =
\pi_m(\last ~ \MCPTrace) \component\) for all \(\component\) where \(\domMap ~ \component = \sealed{\depth''}\)
for any \(\depth''\).

@@

\definition Machine states \(\mach\) and \(\nach\) are {\em \(\components\)-variants} if, for
all \(\component \not \in \components\), \(\mach ~ \component = \nach ~ \component\). We write
this \(\mach \approx_\components \nach\).

\definition Machine state pairs \(\mach,\mach'\) and \(\nach,\nach'\) have the {\em same differences}
if for all components \(\component\) such that \(\mach ~ \component \not = \mach' ~ \component\) or
\(\nach ~ \component \not = \nach' ~ \component\), \(\mach' ~ \component = \nach' ~ \component\).
This is written \(\mach,\mach' \diamond \nach,\nach'\).

\definition Transparency Rule

\definition A system enjoys {\em eager confidentiality} if, for any initial state \(\mach_0\), initial
context \(\context_0\), and initial policy state \(\pol_0\) and any call depth \(\depth\), each segment
\(\MCPTrace\) taken from the induced trace from \(\mach_0,\context_0,\pol_0\) by
\(\prop (\domMap,\depth') = \depth' \geq \depth\) behaves the same as any \(\components\)-variant
as follows.

\begin{itemized}
\item
\item
\item
\end{itemized}
